Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
typo
wording

\subsection{Partial correlation compare favorably with other state-of-the art methods}

@@

The area under the ROC curve is not consistent metric
with respect to the problem statement. We strongly advice to avoid the AUROC
for the assessment of network inference method. An alternative metric would
be to use the area under the precision-recall curve (AUPRC). Those
conclusions are in line with \cite{schrynemackers2013protocols}.

>>>>

\subsection{Partial correlation improves over state-of-the-art methods}

@@

The area under the ROC curve is not consistent metric
with respect to the problem statement. We advice to avoid the AUROC
for the assessment of network inference method. An alternative metric would
be the area under the precision-recall curve (AUPRC). Those
conclusions are in line with \cite{schrynemackers2013protocols}.
